Object Categorization based on RGBD data

### 2014-02-06 Disseration/article.tex
latest changes
added factory class, changing modes to desc, clust, train pred
przeredagowane 1/2
done editing, now have to run some tests
aha

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{cite}

%\setlength{\parskip}{6pt}%
\linespread{1.5}

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}

%opening
\title{Object Categorization based on RGBD data}
\author{Adam Kosiorek}
\bibliographystyle{abbrv}
\begin{document}

\maketitle

\include{streszczenie}
\include{abstract}
\include{introduction} %aka motivation
\include{bow}
\include{libs}
\include{datasets}
\include{architecture}
\include{setup}
\include{experiments}
\include{conclusion}

@@

\end{document}

>>>>

%TODO
%	- run cluster and descriptors tests
%	- find out what's wrong with sift detector
%	- run detector tests
%	- prepare strategy pattern class diagram and describe it
%	- write conclusions
%	- describe libraries
%	- write abstracts
%	- go through introduction
%
%
%

\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{color}
\usepackage[font=footnotesize]{caption}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage{paralist}
\usepackage{tocbibind}
%\usepackage[nottoc,notlof,notlot]{tocbibind}

%\renewcommand{\chaptername}{}
%\renewcommand{\thechapter}{}

\linespread{1.5}

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand\rednote[1]{\textcolor{red}{#1}}

\makeatletter
% Redefine the \chapter* header macro to remove vertical space
\def\@makeschapterhead#1{%
  %\vspace*{50\p@}% Remove the vertical space
  {\parindent \z@ \raggedright
    \normalfont
    \interlinepenalty\@M
    \Huge \bfseries  #1\par\nobreak
    \vskip 20\p@
  }}
\makeatother

\bibliographystyle{abbrv}
\begin{document}

\include{titlepage}
%\include{zyciorys}

\pagestyle{plain}

\include{abstract}

\tableofcontents
\include{introduction}
\include{architecture}
\include{experiments}

\listoffigures
\listoftables

@@

\appendix
\chapter{Source code}
	The source code of the main programme as well as all the scripts and a sample configuration file are included on an attached CD.
\end{document}

### 2014-02-06 Disseration/zyciorys.tex
aha

@@

	I was born on 28 February 1991 in Olsztyn, Poland. I attended 5\superscript{th} Secondary School by the name of ``The Common Europe'' in Olsztyn. I started a Bachelor of Engineering degree on the Faculty of Mechatronics of Warsaw University of Technology on 1 October 2010. I did an internship in Faurecia R\&D S.A. in 2012. In 2013 I started working in IBM Poland Sp. z o.o. where I stayed for 6 months. Then I started working full-time in Samsung R\&D Centre Poland.

@@

>>>>

  \documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{color}
\usepackage[font=footnotesize]{caption}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage{paralist}
\usepackage{tocbibind}
%\usepackage[nottoc,notlof,notlot]{tocbibind}

%\renewcommand{\chaptername}{}
%\renewcommand{\thechapter}{}

\linespread{1.5}

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand\rednote[1]{\textcolor{red}{#1}}

\makeatletter
% Redefine the \chapter* header macro to remove vertical space
\def\@makeschapterhead#1{%
  %\vspace*{50\p@}% Remove the vertical space
  {\parindent \z@ \raggedright
    \normalfont
    \interlinepenalty\@M
    \Huge \bfseries  #1\par\nobreak
    \vskip 20\p@
  }}
\makeatother

\begin{document}

@@

	I was born on 28 February 1991 in Olsztyn, Poland. I attended 5\superscript{th} Secondary School by the name of ``The Common Europe'' in Olsztyn. I started a Bachelor of Engineering degree on the Faculty of Mechatronics of Warsaw University of Technology on 1 October 2010. I did an internship in Faurecia~R\&D~S.A. in 2012. I joined IBM Poland Sp.~z~o.~o. in January, 2013. Then, I started working full-time in Samsung R\&D Centre Poland as a Computer Vision Engineer. I am an avid long distance runner and a keen reader of fantastic literature and thrillers.

@@

\end{document}
